Supplementary Materials

### 2020-05-13 analysis/analysis.Rmd
Edits to supmat

```
at

@@

summary(m_eeg)
```

We will now have at what the model predicts for the average participant (i.e, ignoring the random intercepts). If anybody else would like to suggest over sensible ways to summarise this model, do let me know! I've been trying to use some of the functions from the `tidybayes` package, and they don't (yet?) have much on random effects.

@@

 # Extract samples from model
my_samples$eeg <- get_model_samples(m_eeg)

 # Tidy up a little
 my_models$eeg <- get_model_predictions(my_samples$eeg)

 # Plot
plot_model_output(
  my_models$eeg, d_eeg,
  "Model Fits for the odd-harmonic data from occipital electrodes",
  "orangered3", 
  "log(rms)")
```

@@

```{r threshold_fit_model, cache=TRUE, echo=FALSE}
m_threshold <- brm(data = d_dispthresh, 
                   threshold ~ wg-1 + (1|subject),
                   family = "lognormal", 
                   prior = prior, iter = n_iter,
                   control = list(adapt_delta = 0.99))

summary(m_threshold)
```

```{r, fig.cap ="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}
# Extract samples from model
my_samples$threshold <- get_model_samples(m_threshold)

# Tidy up a little
my_models$threshold <- get_model_predictions(my_samples$threshold)

# Plot
plot_model_output(my_models$threshold, d_dispthresh, 
                  "Model Fits: Psychophysical Data", "orangered3", "threshold (ms)")
```

@@

```{r cache=TRUE, fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}

@@

# Finally, plot everything:
p1 <- plot_comparisons(
  filter(subgroup_comp$threshold, index == 2),
  filter(comp_summary$threshold, index == 2), 
  1, TRUE)
p2 <- plot_comparisons(
  filter(subgroup_comp$threshold, index != 2),
  filter(comp_summary$threshold, index != 2), 
  2, TRUE)

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv") 
both_plts

@@

@@

df %>% gather("measurement", "number", -p) %>%
  mutate(proportion = number/64) %>%
  ggplot(aes(x = p, y = proportion, colour = measurement)) + geom_point() + geom_path() +
  theme_minimal() + ggthemes::scale_color_ptol() +
  xlab("probability of difference given data") + ylab("proportion of subgroup comparisons")

filter(df, p == 0.95)
```

@@

```{r}

my_models <- list()
my_models$full <- brm(data = comp_summary$eeg, mean_value ~ as.numeric(as.character(index))  + normal)

summary(my_models$full)

comp_summary$eeg %>% 
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$full, n = 100) %>%
  ggplot(aes(x =  as.numeric(as.character(index)), y = .value, color = as.factor(normal), group = interaction(.draw, normal))) +
  geom_line(alpha = .2) +
  geom_jitter(data = comp_summary$eeg, aes(x =  as.numeric(as.character(index)), y = mean_value, colour = as.factor(normal), group = 1), width = 0.1, height = 0, alpha = 0.33) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol() + scale_x_continuous(breaks = c(2,3,4,6,8,12)) +
  theme(panel.grid.minor = element_blank())
```

```{r}
my_models <- list()
my_models$full <- brm(data = comp_summary$threshold, mean_value ~ as.numeric(as.character(index))  + normal)

summary(my_models$full)

comp_summary$threshold %>% 
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$full, n = 100) %>%
  ggplot(aes(x =  as.numeric(as.character(index)), y = .value, color = as.factor(normal), group = interaction(.draw, normal))) +
  geom_line(alpha = .2) +
  geom_jitter(data = comp_summary$threshold, aes(x =  as.numeric(as.character(index)), y = mean_value, colour = as.factor(normal), group = 1), width = 0.1, height = 0, alpha = 0.33) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol() + scale_x_continuous(breaks = c(2,3,4,6,8,12))+
  theme(panel.grid.minor = element_blank())
```

@@

```{r fig.cap="Scatter plot showing the correlation between our two measures. Each line is a sample from the posterior of a Bayesian linear regression."}
d %>% 
  modelr::data_grid(rms = seq(-0.2, 0.8, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = index)) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol()
```

>>>>

```

@@

summary(m_eeg)

# Also fit to display duration data so I can display both models together

m_threshold <- brm(data = d_dispthresh, 
                   threshold ~ wg-1 + (1|subject),
                   family = "lognormal", 
                   prior = prior, iter = n_iter,
                   control = list(adapt_delta = 0.99))
```

We will now look at the model's predicts for the average participant (i.e, ignoring the random intercepts).

@@

 # Extract samples from model
my_samples$eeg <- get_model_samples(m_eeg)
my_samples$threshold <- get_model_samples(m_threshold)

 # Tidy up a little
 my_models$eeg <- get_model_predictions(my_samples$eeg)
 my_models$threshold <- get_model_predictions(my_samples$threshold)

 # Plot
plt1 <- plot_model_output(
  my_models$eeg, d_eeg,
  "odd-harmonic data from \noccipital electrodes",
  "orangered3", 
  "log(rms)")

plt2 <- plot_model_output(
  my_models$threshold, d_dispthresh, 
  "Psychophysical Data", 
  "orangered3", 
  "threshold (ms)")

plt1 + plt2 + plot_annotation(title = 'Model Fits:')

```

@@

```{r threshold_fit_model, cache=TRUE, echo=FALSE}
summary(m_threshold)
```

@@

```{r fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}

@@

# Finally, plot everything:
p1 <- plot_comparisons(
  filter(subgroup_comp$threshold, index == 2),
  filter(comp_summary$threshold, index == 2), 
  1, TRUE)

p2 <- plot_comparisons(
  filter(subgroup_comp$threshold, index != 2),
  filter(comp_summary$threshold, index != 2), 
  2, TRUE)

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv") 
both_plts + plot_annotation(title = 'Odd harmonic data from parietal electrodes')

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts + plot_annotation(title = 'Even harmonic data from occipital electrodes')
```

@@

df %>% gather("measurement", "number", -p) %>%
  mutate(proportion = number/64) %>%
  ggplot(aes(x = p, y = proportion, colour = measurement)) + geom_point() + geom_path() +
  theme_minimal() + ggthemes::scale_color_ptol(labels = c("primary EEG", "sensor control EEG", "harmonic control EEG", "psychophysical threshold")) +
  xlab("probability of difference given data") + ylab("proportion of subgroup comparisons")
```

If we take p=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/64 = 87.5% and 49/64 = 76.6% of the comparisons for the primary EEG and display durations repectively. This compares to the $32/64= 50.0% and 22/64 = 34.4% for the control EEG conditions.

@@

```{r}
my_models <- list()
comp_summary$eeg$index <- as.numeric(as.character(comp_summary$eeg$index))
comp_summary$threshold$index <- as.numeric(as.character(comp_summary$threshold$index))

my_models$eeg <- brm(data = comp_summary$eeg, mean_value ~ index * normal)
my_models$disp <- brm(data = comp_summary$threshold, mean_value ~ index * normal)
summary(my_models$eeg)
summary(my_models$disp)
```

We can see that the index of the subgroup relationship has an effect on both the difference in log(rms) and the difference in log(display duration): relationships with a higher index lead to larger differences.

```{r, fig.cap = "The effect of index and normality on log(rms) and log(ms)."}
comp_summary$eeg %>% 
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$eeg, n = 100) %>%
  mutate(model = "primary eeg") -> d_plt_eeg

comp_summary$threshold %>% 
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$disp, n = 100) %>%
  mutate(model = "psychophysical threshold") -> d_plt_disp

d_summary <- bind_rows(comp_summary$threshold %>% mutate(model = "psychophysical threshold"),
                       comp_summary$eeg %>% mutate(model = "primary eeg"))

bind_rows(d_plt_eeg, d_plt_disp) %>%
  ggplot(aes(x =  index, y = .value, color = as.factor(normal), group = interaction(.draw, normal))) +
  geom_line(alpha = .15) +
  facet_wrap(~ model, scales="free_y") + 
  geom_jitter(
    data = d_summary, 
    aes(x =  index, y = mean_value, colour = as.factor(normal), group = 1), width = 0.1, height = 0, alpha = 0.33) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol(labels = c("non-normal", "normal")) + 
  scale_x_continuous("index", breaks = c(2,3,4,6,8,12)) +
  scale_y_continuous("value") +
  theme(panel.grid.minor = element_blank(), legend.title = element_blank()) 
```

@@

```{r fig.cap="Scatter plot showing the correlation between our two measures. Each line is a sample from the posterior of a Bayesian linear regression."}
d %>% 
  modelr::data_grid(rms = seq(-0.2, 0.8, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = as.factor(index))) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol("index")
```
